---
title: "Analysis Code"
output:
  word_document: default
  pdf_document: default
---
load the libraries needed
```{r}
library(ggplot2)
library(ggpubr)
library(scales)
library(ggthemes)
library(performance)
library(lme4)
library(ggcorrplot)
```

Load the data of interest for analysis
```{r}
df <- read.csv("Analysis Data.csv")
df <- df[,-1]

#make the variables into their correct format
df$income <- as.factor(df$income)
df$employment <- as.factor(df$employment)
df$WFH <- as.factor(df$WFH)
df$education <- as.factor(df$education)
df$race <- as.factor(df$race)
df$gender <- as.factor(df$gender)
df$SC <- as.factor(df$SC)
df$BC <- as.factor(df$BC)
df$SAH <- as.factor(df$SAH)

policy <- read.csv("policy.csv")
policy <- policy[,-1]

us <- read.csv("us.csv")
#increase in cases each day is then written as 
new.cases <- diff(us$cases)
us$new.cases <- c(0, new.cases)
```

now create a plot for new cases each day in the US during the study period of 28th Oct 2020 to 1st Feb 2021
```{r}
#subset the us data to around 2020-10-28 to 2021-02-15
us <- us[us$date > as.Date("2020-07-01"),]
us <- us[us$date < as.Date("2021-07-01"),]

g1 <- ggplot(us, aes(x= as.Date(date), y = new.cases)) + geom_bar(stat = "identity", fill="steelblue") + scale_x_date(date_breaks = "months" , date_labels = "%b-%y", name = "Date") + 
    geom_vline(xintercept = as.Date(c("2020-10-28", "2021-02-15")), linetype=2, colour="black") + 
    ylab("New Cases") + 
    scale_y_continuous(limits = c(-24000,300800), labels = comma) + 
    theme_classic() 
g1

ggsave("us new cases by date.pdf", plot = g1, width = 2500, height = 1400,
  units = "px",)
```

Calculating the numbers of NAs in the df file
```{r}
table(df$depression)
table(df$anxiety)
table(df$income)
table(df$employment)
table(df$WFH)

#making non-replies into NA for later analysis
df$depression[df$depression == "-99" | df$depression == "-88"] <- NA
df$anxiety[df$anxiety == "-99" | df$anxiety == "-88"] <- NA
df$income[df$income == "-99" | df$income == "-88"] <- NA
df$employment[df$employment == "-99" | df$employment == "-88"] <- NA
df$WFH[df$WFH == "-99" | df$WFH == "-88"] <- NA
```

calculate the ICC for HPS data
```{r}
m0 <- lmer(depression~(1|state),data=df) 
m00 <- lmer(anxiety~(1|state),data=df) 
icc(m00)
icc(m0)
```

Inspecting multicollinearity in policies at the state level
```{r}
#the column names of policy data
colnames(policy)[3] <- "School Closure"
colnames(policy)[4] <- "Business Closure"
colnames(policy)[5] <- "SAH Order"
#a simple correlation matrix of the three independent variables 
#correlation matrix stored in a matrix object
corr <- round(cor(policy[,c(3,4,5)]), 3)
head(corr)
ggcorrplot(corr, hc.order = TRUE, type = "lower",
   lab = TRUE, digits = 4, ggtheme = ggplot2::theme_classic())
```

modelling for the outcome of depression and anxiety for all respondents, SAH order and BUS
```{r}
m1.1 <- lm(depression ~ SAH + BC + income + gender + education + age + new.cases + race + new.deaths + period + BC*employment + BC*WFH, df)
summary(m1.1)

m1.2 <- lm(anxiety ~ SAH + BC + income + gender + education + age + new.cases + race + new.deaths + period + BC*employment + BC*WFH, df)
summary(m1.2)

m2.1 <- lm(depression ~ SAH*BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, df)
summary(m2.1)

m2.2 <- lm(anxiety ~ SAH*BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, df)
summary(m2.2)

```

subset df into a data which only includes observations whose child is > 0, and conduct the same models as the above
```{r}
df_parents <- df[df$child == 1, ]

m3.1 <- lm(depression ~ SAH + BC + SC + income + gender + education + age + new.cases + race + new.deaths + period + SC*employment + SC*WFH, df_parents)
summary(m3.1)

m3.2 <- lm(anxiety ~ SAH + BC + SC + income + gender + education + age + new.cases + race + new.deaths + period + SC*employment + SC*WFH, df_parents)
summary(m3.2)

m4.1 <- lm(depression ~ SAH*SC + BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, df_parents)
summary(m4.1)

m4.2 <- lm(anxiety ~ SAH*SC + BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, df_parents)
summary(m4.2)

```

plot residual plots to see test if there's heteroskedasticity. This is for Model 1 and Model 2.
```{r}
complete_df <- na.omit(df)

#residuals for Model 1
complete_df$m1_res.dep <- resid(lm(depression ~ SAH + BC + income + gender + education + age + new.cases + race + new.deaths + period + BC*employment + BC*WFH, complete_df))

complete_df$m1_res.anx <- resid(lm(anxiety ~ SAH + BC + income + gender + education + age + new.cases + race + new.deaths + period + BC*employment + BC*WFH, complete_df))

p1 <- ggplot(complete_df,aes(x=SAH, y=m1_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 1 Depression Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p2 <- ggplot(complete_df,aes(x=SAH, y=m1_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 1 Anxiety Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p3 <- ggplot(complete_df,aes(x=BC, y=m1_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 1 Depression Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p4 <- ggplot(complete_df,aes(x=BC, y=m1_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 1 Anxiety Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

#create a residual plot for Model 1
ggarrange(p1, p3, p2, p4,
          ncol = 2, nrow = 2)

#residuals for Model 2
complete_df$m2_res.dep <- resid(lm(depression ~ SAH*BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, complete_df))

complete_df$m2_res.anx <- resid(lm(anxiety ~ SAH*BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, complete_df))

p1 <- ggplot(complete_df,aes(x=SAH, y=m2_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 2 Depression Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p2 <- ggplot(complete_df,aes(x=SAH, y=m2_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 2 Anxiety Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p3 <- ggplot(complete_df,aes(x=BC, y=m2_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 2 Depression Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p4 <- ggplot(complete_df,aes(x=BC, y=m2_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 2 Anxiety Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

#creating a residual plot for Model 2
ggarrange(p1, p3, p2, p4,
          ncol = 2, nrow = 2)
```

This is for Model 3 and Model 4.
```{r}
complete_df_parents <- na.omit(df_parents)

#residuals for Model 3
complete_df_parents$m3_res.dep <- resid(lm(depression ~ SAH + BC + SC + income + gender + education + age + new.cases + race + new.deaths + period + SC*employment + SC*WFH, complete_df_parents))

complete_df_parents$m3_res.anx <- resid(lm(anxiety ~ SAH + BC + SC + income + gender + education + age + new.cases + race + new.deaths + period + SC*employment + SC*WFH, complete_df_parents))

p5 <- ggplot(complete_df_parents,aes(x=SAH, y=m3_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 3 Depression Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p6 <- ggplot(complete_df_parents,aes(x=SAH, y=m3_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 3 Anxiety Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p7 <- ggplot(complete_df_parents,aes(x=BC, y=m3_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 3 Depression Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p8 <- ggplot(complete_df_parents,aes(x=BC, y=m3_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 3 Anxiety Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p9 <- ggplot(complete_df_parents,aes(x=SC, y=m3_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 3 Depression Residual", x="SC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p10 <- ggplot(complete_df_parents,aes(x=SC, y=m3_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 3 Anxiety Residual", x="SC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

#the residual plot for Model 3
ggarrange(p5, p7, p9, p6, p8, p10,
          ncol = 3, nrow = 2)

#residuals for Model 4 
complete_df_parents$m4_res.dep <- resid(lm(depression ~ SAH*SC + BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, complete_df_parents))

complete_df_parents$m4_res.anx <- resid(lm(anxiety ~ SAH*SC + BC + income + gender + education + age + new.cases + race + new.deaths + period + employment + WFH, complete_df_parents))

p5 <- ggplot(complete_df_parents,aes(x=SAH, y=m4_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 4 Depression Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p6 <- ggplot(complete_df_parents,aes(x=SAH, y=m4_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 4 Anxiety Residual", x="SAH") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p7 <- ggplot(complete_df_parents,aes(x=BC, y=m4_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 4 Depression Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p8 <- ggplot(complete_df_parents,aes(x=BC, y=m4_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 4 Anxiety Residual", x="BC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p9 <- ggplot(complete_df_parents,aes(x=SC, y=m4_res.dep)) +
  geom_boxplot() + 
  labs(y="Model 4 Depression Residual", x="SC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

p10 <- ggplot(complete_df_parents,aes(x=SC, y=m4_res.anx)) +
  geom_boxplot() + 
  labs(y="Model 4 Anxiety Residual", x="SC") +
  theme_clean() +
  theme(plot.background = element_rect(fill = "transparent", color = NA))

#residual plot for Model 4
ggarrange(p5, p7, p9, p6, p8, p10,
          ncol = 3, nrow = 2)

```

Data Table shown in Appendices:

Descriptive Statistics for All Variables:
```{r}
#1 df's control variables
table(df$depression)
table(df$anxiety)
table(df$SAH)
table(df$BC)
table(df$SC)
table(df$income)
table(df$gender)
table(df$education)
table(df$employment)
table(df$WFH)
table(df$race)

#new cases from state levels
mean(policy$new.cases[policy$week == 1])
sd(policy$new.cases[policy$week == 1])

mean(policy$new.cases[policy$week == 2])
sd(policy$new.cases[policy$week == 2])

mean(policy$new.cases[policy$week == 3])
sd(policy$new.cases[policy$week == 3])

mean(policy$new.cases[policy$week == 4])
sd(policy$new.cases[policy$week == 4])

mean(policy$new.cases[policy$week == 5])
sd(policy$new.cases[policy$week == 5])

mean(policy$new.cases[policy$week == 6])
sd(policy$new.cases[policy$week == 6])

mean(policy$new.cases[policy$week == 7])
sd(policy$new.cases[policy$week == 7])

mean(policy$new.deaths[policy$period == 1])
sd(policy$new.deaths[policy$period == 1])

mean(policy$new.deaths[policy$period == 2])
sd(policy$new.deaths[policy$period == 2])

mean(policy$new.deaths[policy$period == 3])
sd(policy$new.deaths[policy$period == 3])

mean(policy$new.deaths[policy$period == 4])
sd(policy$new.deaths[policy$period == 4])

mean(policy$new.deaths[policy$period == 5])
sd(policy$new.deaths[policy$period == 5])

mean(policy$new.deaths[policy$period == 6])
sd(policy$new.deaths[policy$period == 6])

mean(policy$new.deaths[policy$period == 7])
sd(policy$new.deaths[policy$period == 7])
```














